\documentclass[11pt,a4paper]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{setspace} % For spacing
\usepackage{times} % Use Times New Roman font

\renewcommand{\baselinestretch}{1.5} % Line spacing

\begin{document}

% Title
\begin{center}
    {\Large \textbf{Statement of Purpose}}\\[10pt]
    {\large Luka Tadic}\\[5pt]
    {\normalsize ltadic03@yahoo.com | +49 175 729 4494 | Buchauerstraße 18/2, 88348 Bad Saulgau}
\end{center}

% Introduction
\section*{Introduction}
I am currently completing my Bachelor's degree in Electrical Engineering - Vehicle Electronics and am planning to continue with a Master's degree in Electrical Engineering and Embedded Systems. My interest in embedded systems and electrical engineering stems from my practical experience and academic background. This master's program will allow me to expand my knowledge, giving me a broader horizon and more career opportunities in the future.

% Academic Background
\section*{Academic Background}
I am pursuing my Bachelor's degree in cooperation with DHBW Ravensburg, where I balance academic coursework with practical work at Kramer-Werke GmbH. This dual education system has provided me with hands-on experience in electrical engineering and vehicle electronics. During my time at Kramer-Werke GmbH, I have worked on several significant projects, including the development of a circuit diagram for the company's Smart Attach function, which will be presented at future fairs. Additionally, I have contributed to the rework and testing of a new drive system for one of the company's vehicles as a proof of concept for upcoming vehicle models. My current German grade at DHBW Ravensburg is 2.8, though I have yet to complete my Bachelor's thesis and remaining modules, leaving room for further improvement.

% Research Interests
\section*{Research Interests}
While my Bachelor's studies introduced embedded systems, the topic was not covered in depth. This gap in my knowledge has fueled my enthusiasm to explore the field further. I am particularly interested in embedded systems applications in the automotive sector, including electric vehicles and alternative engine options. I believe embedded systems are a crucial part of modern automotive innovations, and I am eager to delve deeper into their design and implementation.

% Work Experience
\section*{Work Experience}
My work at Kramer-Werke GmbH has been instrumental in shaping my technical and problem-solving skills. By working on circuit development and vehicle drive system testing, I have gained insights into real-world engineering challenges and their solutions. This experience has reinforced my decision to specialize in embedded systems, as I recognize the growing importance of efficient, reliable, and intelligent system designs in the automotive industry.

% Career Goals
\section*{Career Goals}
In the future, I plan to work in the automotive sector, particularly in the field of electric vehicles and alternative engine technologies. I believe that this area holds immense potential for innovation and sustainable advancements. By expanding my knowledge in electrical engineering and embedded systems, I aim to contribute to the development of smarter, more efficient vehicle technologies that will shape the future of mobility.

% Why This Program?
\section*{Why This Program?}
The Master of Engineering in Electrical Engineering and Embedded Systems at Ravensburg-Weingarten University aligns perfectly with my aspirations. The program's emphasis on embedded computing, signal processing, and control systems, along with its project-oriented approach, will provide me with the necessary expertise to excel in my field. Additionally, the international environment and collaboration opportunities make it an ideal place to develop my technical and interdisciplinary skills.

% Conclusion
\section*{Conclusion}
With a strong foundation in electrical engineering and vehicle electronics, coupled with hands-on experience at Kramer-Werke GmbH, I am eager to take the next step in my academic and professional journey. This Master's program will enable me to acquire specialized knowledge, enhance my problem-solving abilities, and contribute meaningfully to the future of automotive technology. I am excited about the opportunities this program presents and look forward to becoming a part of Ravensburg-Weingarten University's academic community.

\end{document}
